Democracy, Public Support, and Measurement Uncertainty

### 2021-06-01 paper/dcpo_demsupport.Rmd
adding visualization for full uncertain

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = FALSE, fig.width=7.5, fig.height=10}

@@

>>>>

```{r visualizeFullUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=10}

@@

```{r visualizedAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = FALSE, fig.width=7, fig.height=10}

result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsAPSRfullUncertain.RDS"))
result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSRfullUncertain.RDS"))
